Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd

plot_path <- here::here("other", "plots", "election_map.png")

#read in cleaned data
cleaned_poll_data <-
  read_csv(file = here("data/cleaned_poll_data.csv"), 
           show_col_types = FALSE)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
election_results <- data.frame(
  Metric = c("Chance of Winning", "Average Electoral Votes"),
  Harris = c("68.8%", "279.21"),
  Trump = c("30.1%", "258.79"),
  stringsAsFactors = FALSE
)

election_results %>%
  kable("html", caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold

@@

```{r}
#| echo: false
#| warning: false
#| message: false
knitr::include_graphics(plot_path)

>>>>

plot_path <- here::here("other", "plots", "election_map.pdf")

#read in cleaned data
cleaned_poll_data <-
  read_csv(file = here("data/cleaned_poll_data.csv"), 
           show_col_types = FALSE)
swing_probs <- read_csv(file = here("other/plots/swing_states_probabilities.csv"))
```

@@

```{r}
#| fig-cap: Election Prediction Results
#| echo: false
#| warning: false
#| message: false

#| echo: false
#| warning: false
#| message: false
election_results <- data.frame(
  Metric = c("Chance of Winning", "Average Electoral Votes"),
  Harris = c("68.8%", "279.21"),
  Trump = c("30.1%", "258.79"),
  stringsAsFactors = FALSE
)

election_results %>%
  kable(caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold

@@

```{r}
#| fig-cap: Election Map
#| echo: false
#| warning: false
#| message: false
knitr::include_graphics(plot_path)
